The Effect of Elections and Prime Ministers on Discussion in the Australian Federal Parliament (1901--2018)

### 2018-12-11 outputs/docs/events/slides/slides.Rmd
Add Rostock slides

---
title: The Effect of Events on Discussion in the Australian Federal Parliament (1901--2017)
subtitle: 
author:
- Monica Alexander, University of Toronto\newline
- \textbf{Rohan Alexander, Australian National University}
date: 22 November 2018
institute: Presentation at the University of Toronto Political Behaviour Group, Toronto, Canada.
output: binb::metropolis
# output: ioslides_presentation
fontsize: 12pt
---

@@

- Create a dataset of what was said in the Australian Federal Parliament from 1901 through to 2017 based on available public records. 
- Use a correlated topic model to reduce dimemsionality.
- Analyse the effect of various events using a Bayesian hierarchical Dirichlet model.

<div class="notes">
Test
</div>

@@

- Changes in government tend be associated with topic changes even when the party in power does not change.
- Elections that do not result in a change in government are rarely associated with topic changes.
- The effect of events is much more pronounced in the second half of our sample, and especially in the past two decades.

@@

## Hansard
- A daily text record called Hansard of what was said in the Australian Federal Parliament has been made available since it was established in 1901. It's not vertatim, but it's pretty close.
- Hansard records have been used in other counties but not really at scale in Australia.
- Daily PDFs are available online and these are considered the official release. 
- There are 14,551 days of publicly available Hansard records across both chambers of the Australian Federal Parliament.

@@

## Analysis model - Set-up
- Define $\theta_{dp}$ to be the proportion of topic of topic $p$ on day $d$. Note that the $\theta_{d,1:P}$ for $p = 1,2,\dots P=40$ are equal to the estimated values of $\theta_d$ from the CTM. 
- We assume that the majority of variation in topics is across sitting periods $s$, where a sitting period is defined as any group of days that are less than one week apart. Using this definition, there are a total of 745 sitting periods over the period 1901 to 2017 inclusive.

>>>>

---
title: The Effect of Elections and Prime Ministers on Discussion in the Australian Federal Parliament (1901--2018)
subtitle: 
author:
- Monica Alexander, University of Toronto\newline
- \textbf{Rohan Alexander, Australian National University}
date: 11 December 2018
institute: Presentation at the Max Planck Institute for Demographic Research, Rostock, Germany.
output: binb::metropolis
# output: ioslides_presentation
fontsize: 12pt
---

@@

- Create a dataset of what was said in the Australian Federal Parliament from 1901 through to 2018 based on available public records. 
- Use a correlated topic model to reduce dimemsionality.
- Analyse the effect of various events using a Bayesian hierarchical Dirichlet model.

@@

- Changing the prime minister tends be associated with topic changes even when the party in power does not change.
- Elections that do not result in a change in prime minister are rarely associated with topic changes.
- The effect of these types of events is much more pronounced in the second half of our sample, and especially in the past two decades.

@@

## Hansard
- A daily text record called Hansard of what was said in the Australian Federal Parliament has been made available since it was established in 1901. It's not vertatim, but it's pretty close.
- Hansard records have been used in other counties but not really at scale in Australia.
- Daily PDFs are available online and these are considered the official release. 
- There are 14,680 days of publicly available Hansard records across both chambers of the Australian Federal Parliament.

@@

## Analysis model - Set-up
- Define $\theta_{dp}$ to be the proportion of topic of topic $p$ on day $d$. Note that the $\theta_{d,1:P}$ for $p = 1,2,\dots P=80$ are equal to the estimated values of $\theta_d$ from the CTM. 
- We assume that the majority of variation in topics is across sitting periods $s$, where a sitting period is defined as any group of days that are less than one week apart. Using this definition, there are 745 sitting periods over the period 1901 to 2018 inclusive.
